---
title: "Legendary Pokemon"
author: "Jason Lee"
output: html_document
---

### Overview

For this analysis I'm going to dive into Pokemon ratings and whether or not they are marked as being "Legendary". I will focus on creating a logistic model and a desicion tree model to help predict whether or not a pokemon will be Legendary based on specific variable parameters

### Sample of Data
```{r setup,include=TRUE, echo=FALSE, message= FALSE, warning = FALSE}
knitr::opts_chunk$set(include = FALSE)
library(ggplot2)
library(gplots)
library(readr)
library(rpart)
library(ROCR)
library(rpart.plot)
```


```{r summary, include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
pkdf <- read.csv("Pokemon.csv")
head(pkdf)
```


### Logistic Model

##### Test with all the dependent variables first. The model could be improved.
```{r 1st logistic, include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
pk_logit_model <- glm(Legendary ~ Attack + Defense + Sp_Atk + Sp_Def + HP + Speed, data = pkdf, family = "binomial")
summary(pk_logit_model)
```

##### Test with deleteing Defense variable:
```{r 2nd logistic, include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
pk_logit_model <- glm(Legendary ~ Attack + Sp_Atk + Sp_Def + HP + Speed, data = pkdf, family = "binomial")
summary(pk_logit_model)
```

##### Test with deleteing Speed variable:
```{r 3rd logistic, include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
pk_logit_model <- glm(Legendary ~ Attack + Sp_Atk + Sp_Def + HP, data = pkdf, family = "binomial")
summary(pk_logit_model)
```
We can see from this model that deleteing SPEED produced a good mdoel.

Looking at the results from this model we can interpret the coeffiencent of Attack as if Attack increases by 1 point, chance of this Pokemon being legendary increases by 3.04%

```{r Attack}
exp(0.029982)-1
```



### Decision Model

Putting all the same variables in one tree.
```{r tree,include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
pk_tree_model <- rpart(Legendary ~  Attack + Sp_Atk + Sp_Def + HP, data = pkdf, method = "class")  #, control=rpart.control(minsplit=50, cp=0.018))
rpart.plot::rpart.plot(pk_tree_model, type = 1, extra=1, box.palette =c("pink", "green"), branch.lty=3, shadow.col = "gray")
```

```{r tree summary}
summary(pk_tree_model)
```


```{r tree plot,include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
plotcp(pk_tree_model)
```

### Comparing the Logisitic Model and the Decision Tree

```{r predict, message=FALSE, warning=FALSE, include=FALSE}
#predict with logistic regression
pk_predict_logit <- predict(pk_logit_model, pkdf, type="response")
print(pk_predict_logit)
```

```{r log pokemon 59}
pk_predict_logit[59]
```

```{r log pokemon 799}
pk_predict_logit[799]
```

```{r tree predict, message=FALSE, warning=FALSE, include=FALSE}
#predict with tree
pk_predict_tree <- predict(pk_tree_model, pkdf, type="prob")
print(pk_predict_tree)
```

```{r results, include=TRUE, echo=FALSE, message=FALSE, warning = FALSE}
#Storing Model Performance Scores
pk_logit_prediction <- prediction(pk_predict_logit, pkdf$Legendary)
pk_tree_prediction <- prediction(pk_predict_tree[,2], pkdf$Legendary) 

#Let's get performance.
pk_performance_logit <- performance(pk_logit_prediction,"tpr","fpr")
pk_performance_tree <- performance(pk_tree_prediction,"tpr","fpr")

#Let's plot and compare. The more area under the curve, the better the model is.
plot(pk_performance_logit,col="blue",lty=3, lwd=3)
plot(pk_performance_tree,col="black",lty=3, lwd=3, add=TRUE)
#logistic regression wins!
```

### Final Thoughts

If we use the model we can try predict two Pokemon ID numbers and determine if they are Legendary.

  Pokemon 59\
    - Model Prediction: Most likely not legendary\
    - Actual: Not legendary
  
  Pokemon 799\
    - Model Prediction: Most likely legendary\
    - Actual: Legendary

Looking at both thesse line chart we can see that Logisitic Model performs better and therefore is a better choice to use when predicting if a Pokemon will be Legendary.